Figures from: Impacts of host availability and temperature on mosquito-borne parasite transmission

### 2023-12-13 manuscript-figures.Rmd
small edits to figures

```{r fig-3_MosquitoThermalTraits, dev = c('pdf','svg', 'png'),  out.width='100%', fig.height=6, fig.width=9, fig.align='center', fig.cap='\\label{fig:MosquitoThermalTraits} Thermal performance curves (TPCs) for the mosquito and parasite traits used in our model. Curves are shown in color for each of the five systems we considered. Temperatures vary from 10\textdegree C to 35\textdegree C to encompass the full thermal niche of all mosquito species considered in this study (defined as the range of temperatures at which all traits for a given species are positive). Each trait is a unimodal function of temperature except for the lifespan of \\textit{Culex quinquefasciatus} (d). Recruitment rate (a) is derived from a sub-model of immature mosquito population dynamics in equations  (2.6) and (2.7. The \\textit{Aedes aegypti} and DENV and \\textit{Ae. aegypti} and ZIKV recruitment rate (a) and maximum biting frequency (b) curves overlap because infection is assumed to not affect these traits (but see Tesla et al. (2018)). All functions and parameters for generating these curves are derived from Mordecai et al., 2013, 2017, 2019; Tesla et al., 2018; Shocket et al., 2020. Shown here are the median values of the mosquito traits with respect to their TPC hyperparameter posterior distributions. A full description of how these curves were obtained is available in Appendix S2: Section S1.'}
## Set up plot dataframe
MosqThermTraits_df <- median.Vec %>%
  # Mortality rate
  mutate(muV = 1 / lf) %>%
  # Recruitment rate
  mutate(lambdaV = V0 * muV) %>%
  # Prob. of surviving EIP
  mutate(P_EIP = exp(-muV / etaV)) %>%
  # Prob. of larval survival
  # Select relevant traits and parameters
  dplyr::select(Temperature, system_ID, sigmaV, sigmaV_f, rhoL, lf, deltaL, P_EIP, betaV) %>%
  # Turn all columns except Temperature and system_ID into variables
  melt(id = c("Temperature", "system_ID")) %>%
  mutate(variable = factor(variable,
                           levels = c("lf", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "P_EIP", "betaV"),
                           labels = c(
                             TeX("(a) Adult lifespan: $1/\\mu_V$ (days)"),
                             TeX("(b) Biting frequency: $\\sigma_V$ (day$^{-1}$)"),
                             TeX("(c) Eggs per female per day: $\\sigma_V f$"),
                             TeX("(d) Immature mosquito development rate: $\\rho_L$ (day$^{-1}$)"),
                             TeX("(e) Probability of immature mosquito survival: $\\delta_L$"),
                             TeX("(f) Probability of surviving EIP: $\\theta_V$"),
                             TeX("(g) Vector competence: $\\beta_V$")
                           )
  )) %>%
  group_by(Temperature, system_ID)

@@

# Supplementary Figures

@@

Topt_estimates_median <- left_join(ToptRM_base_estimates, Topt0_base_estimates) %>%
  select(system_ID, Topt_RM, Topt_0) %>%
  mutate(Topt_diff = Topt_RM - Topt_0) %>%
  mutate(prop_Topt_diff = abs(Topt_diff) / Topt_RM)
```

@@

```{r fig-S8_R0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_unc} The local sensitivity of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$ and $K_H$. Generally, $\\mathcal{R}_0$ is most sensitive to biting frequency, the probability of surviving the extrinsic incubation period, and vector competence. Shown here are the median values of the derivative of $\\mathcal{R}_0$ with respect to each focal mosquito trait across the mosquito trait TPC hyperparameter posterior distributions. Sensitivity values are shown on a logarithmic scale with solid lines indicating positive values and dotted lines indicating negative. Temperatures are restricted to those at which the median of $\\mathcal{R}_0$ is positive for the given system. '}
KH_vals <- c(1, 100)

@@

# NB: in order to produce an R0 TPC, "overall" derivative should go from positive to negative
plot.dR0dk <- dR0dk.df %>%
  # filter(focal_var %in% c("Overall")) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = norm_median, color = focal_var, 
             # linetype = (as.factor(sign_median))
  )) +
  geom_line(lwd = 0.5) +
  geom_hline(yintercept = 0, lwd = 0.25) +
  scale_color_manual(
    name = "Focal trait:",
    values = rev(c(c4a("misc.okabe", 7), "black"))
  ) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(
    name = unname(TeX("Normalized local sensitivity of $\\,R_0$ to temperature")),
    # limits = c(-1, 1),
    # limits = 10^c(-4, 4),
    # breaks = 10^(seq(-4, 4)),
    # labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$", "$10^4$")),
    # trans = "log10",
    expand = c(0, 0)
  ) +
  # scale_linetype_manual(
  #   name = "Sign of sensitivity:",
  #   values = c(1, 3),
  #   breaks = c(1, -1),
  #   labels = c("Positive", "Negative")
  # ) +
  facet_rep_grid(
    rows = vars(KH, sigmaH),
    cols = vars(system_label),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
      KH = as_labeller(appender_KH, default = label_parsed)
    ),
    scales = "free"
  ) +
  guides(linetype = guide_legend(
    title.position = "left",
    title.vjust = 0.5,
    direction = "vertical"
  )) +
  theme_minimal_hgrid(10) +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.position = "bottom",
    legend.justification = 0.5,
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

plot.comp_dR0dk <- comp_dR0dk.df %>%
  # filter(focal_var %in% c("Overall")) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = prop_sens, fill = focal_var, color = focal_var,
             # linetype = (as.factor(sign_median))
  )) +
  # geom_area() +
  geom_line(lwd = 1) +
  geom_hline(yintercept = 0, lwd = 0.25) +
  scale_color_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(
    name = unname(TeX("Contributions to overall local sensitivity of $\\,R_0$")),
    # limits = c(-100, 100),
    # limits = c(-0.2, 0.1),
    # limits = 10^c(-4, 4),
    # breaks = 10^(seq(-4, 4)),
    # labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$", "$10^4$")),
    # trans = "log10",
    expand = c(0, 0)
  ) +
  # scale_linetype_manual(
  #   name = "Sign of sensitivity:",
  #   values = c(1, 3),
  #   breaks = c(1, -1),
  #   labels = c("Positive", "Negative")
  # ) +
  facet_rep_grid(
    rows = vars(sigmaH, KH),
    cols = vars(system_label),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
      KH = as_labeller(appender_KH, default = label_parsed)
    ),
    scales = "free"
  ) +
  guides(linetype = guide_legend(
    title.position = "left",
    title.vjust = 0.5,
    direction = "vertical"
  )) +
  theme_minimal_hgrid(10) +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.position = "bottom",
    legend.justification = 0.5,
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

plot.comp_dR0dk
```

``` {r}
# 1. change in non-normalized sensitivity as KH: 1 to 100
compzoom_dR0dk.df_1 <- dR0dk.df %>%
  filter(sigmaH == 10, focal_var != "Overall") %>% 
  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, median) %>%
  pivot_wider(names_from = KH, values_from = median) %>%
  mutate(abs_comp = `1` - `100`)

# 2. Absolute change in non-normalized sensitivity as KH: 1 to 100
compzoom_dR0dk.df_2 <- dR0dk.df %>%
  filter(sigmaH == 10, focal_var != "Overall") %>% 
  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, median) %>%
  pivot_wider(names_from = KH, values_from = median) %>%
  mutate(abs_comp = abs(`1` - `100`))

# 3. Proportional change in non-normalized sensitivity as KH: 1 to 100
compzoom_dR0dk.df_3 <- dR0dk.df %>%
  filter(sigmaH == 10, focal_var != "Overall") %>% 
  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, median) %>%
  pivot_wider(names_from = KH, values_from = median) %>%
  mutate(abs_comp = (`1` - `100`)/(`1`+1))

# 4. Proportional change in non-normalized sensitivity as KH: 1 to 100
compzoom_dR0dk.df_4 <- dR0dk.df %>%
  filter(sigmaH == 10, focal_var != "Overall") %>% 
  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, median) %>%
  pivot_wider(names_from = KH, values_from = median) %>%
  mutate(temp_comp = `1` - `100`) %>% 
  group_by(system_ID, Temperature) %>% 
  mutate(total_comp = sum(temp_comp),
         abs_comp = temp_comp / sum(temp_comp))

compzoom_dR0dk.df <- comp_dR0dk.df %>%
  filter(sigmaH == 10) %>% 
  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, prop_sens) %>%
  pivot_wider(names_from = KH, values_from = prop_sens) %>%
  mutate(abs_comp = abs(`1`) - abs(`100`))

plot.compzoom_dR0dk <- compzoom_dR0dk.df %>% 
  # filter(focal_var %in% c("Parasite development rate", "Adult mortality rate", "Biting frequency")) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = abs_comp, fill = focal_var, color = focal_var,
             # linetype = (as.factor(sign_median))
  )) +
  # geom_area() +
  # geom_smooth(se = FALSE) +
  geom_line(lwd = 1) +
  geom_hline(yintercept = 0, lwd = 0.25) +
  scale_color_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(
    name = unname(TeX("Change in contributions to overall local sensitivity of $\\,R_0$ \n  from $\\,K_H = 1$ to $\\,K_H = 10$ ")),
    # limits = c(-100, 100),
    # limits = c(-0.2, 0.1),
    # limits = 10^c(-4, 4),
    # breaks = 10^(seq(-4, 4)),
    # labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$", "$10^4$")),
    # trans = "log10",
    expand = c(0, 0)
  ) +
  # scale_linetype_manual(
  #   name = "Sign of sensitivity:",
  #   values = c(1, 3),
  #   breaks = c(1, -1),
  #   labels = c("Positive", "Negative")
  # ) +
  facet_rep_grid(
    rows = vars(sigmaH),
    cols = vars(system_label),
    labeller = labeller(
      system_label = sens_labels,
      # sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
      # KH = as_labeller(appender_KH, default = label_parsed)
    ),
    scales = "free"
  ) +
  guides(linetype = guide_legend(
    title.position = "left",
    title.vjust = 0.5,
    direction = "vertical"
  )) +
  theme_minimal_hgrid(10) +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.position = "bottom",
    legend.justification = 0.5,
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

plot.compzoom_dR0dk
```

>>>>

```{r fig-3_MosquitoThermalTraits, dev = c('pdf','svg', 'png'),  out.width='100%', fig.height=6, fig.width=9, fig.align='center', fig.cap='\\label{fig:MosquitoThermalTraits} Thermal performance curves (TPCs) for the mosquito and parasite traits used in our model. Curves are shown in color for each of the five systems we considered. Temperatures vary from 10\textdegree C to 35\textdegree C to encompass the full thermal niche of all mosquito species considered in this study (defined as the range of temperatures at which all traits for a given species are positive). Each trait is a unimodal function of temperature except for the lifespan of \\textit{Culex quinquefasciatus} (d). Recruitment rate (a) is derived from a sub-model of immature mosquito population dynamics in equations  (2.6) and (2.7. The \\textit{Aedes aegypti} and DENV and \\textit{Ae. aegypti} and ZIKV recruitment rate (a) and maximum biting frequency (b) curves overlap because infection is assumed to not affect these traits (but see Tesla et al. (2018)). All functions and parameters for generating these curves are derived from Mordecai et al., 2013, 2017, 2019; Tesla et al., 2018; Shocket et al., 2020. Shown here are the median values of the mosquito traits with respect to their TPC hyperparameter posterior distributions. A full description of how these curves were obtained is available in Appendix S2: Section S1.'}
## Set up plot dataframe
MosqThermTraits_df <- median.Vec %>%
  # Mortality rate
  mutate(muV = 1 / lf) %>%
  # Recruitment rate
  mutate(lambdaV = V0 * muV) %>%
  # Prob. of surviving EIP
  mutate(P_EIP = exp(-muV / etaV)) %>%
  # Prob. of larval survival
  # Select relevant traits and parameters
  dplyr::select(Temperature, system_ID, sigmaV, sigmaV_f, rhoL, lf, deltaL, P_EIP, betaV) %>%
  # Turn all columns except Temperature and system_ID into variables
  melt(id = c("Temperature", "system_ID")) %>%
  mutate(variable = factor(variable,
                           levels = c("lf", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "P_EIP", "betaV"),
                           labels = c(
                             TeX("(a) Adult lifespan: $1/\\mu_V$ (days)"),
                             TeX("(b) Biting frequency: $\\sigma_V$ (day$^{-1}$)"),
                             TeX("(c) Eggs per female per day: $\\sigma_V f$"),
                             TeX("(d) Mosquito development rate: $\\rho_L$ (day$^{-1}$)"),
                             TeX("(e) Prob. of immature mosquito survival: $\\delta_L$"),
                             TeX("(f) Probability of surviving EIP: $\\theta_V$"),
                             TeX("(g) Vector competence: $\\beta_V$")
                           )
  )) %>%
  group_by(Temperature, system_ID)

@@

KH_vals <- c(1, 100)
sigmaH_val <- 10

data.dR0dT <- data.dR0dvar %>%
  filter((KH %in% KH_vals & sigmaH == sigmaH_val) | (KH == 100 & is.infinite(sigmaH)))

temp_lims <- select(data.R0, system_ID, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
  filter(KH %in% KH_vals & sigmaH %in% c(sigmaH_val, Inf)) %>%
  filter(!is.na(median_R0), median_R0 > eps) %>%
  group_by(system_ID) %>% 
  summarise(min_Temp = min(Temperature),
            max_Temp = max(Temperature))

plot.comp_dR0dk <- comp_dR0dk.df %>%
  filter(is.finite(sigmaH)) %>% 
  # filter(focal_var %in% c("Overall")) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = prop_sens, fill = focal_var, color = focal_var,
  )) +
  # geom_area() +
  geom_line(lwd = 1) +
  geom_hline(yintercept = 0, lwd = 0.25) +
  scale_color_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(
    name = unname(TeX("Contributions to overall local sensitivity of $\\,R_0$")),
    expand = c(0, 0)
  ) +
  facet_rep_grid(
    rows = vars(sigmaH, KH),
    cols = vars(system_label),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
      KH = as_labeller(appender_KH, default = label_parsed)
    ),
    scales = "free"
  ) +
  guides(linetype = guide_legend(
    title.position = "left",
    title.vjust = 0.5,
    direction = "vertical"
  )) +
  theme_minimal_hgrid(10) +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.position = "bottom",
    legend.justification = 0.5,
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

# plot.comp_dR0dk

compzoom_dR0dk.df <- comp_dR0dk.df %>%
  filter(sigmaH == sigmaH_val) %>% 
  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, prop_sens) %>%
  pivot_wider(names_from = KH, values_from = prop_sens) %>%
  mutate(abs_comp = `100` - `1`)

plot.compzoom_dR0dk <- compzoom_dR0dk.df %>% 
  ggplot(aes(x = Temperature, y = abs_comp, fill = focal_var, color = focal_var,
  )) +
  geom_line(lwd = 1) +
  geom_hline(yintercept = 0, lwd = 0.25) +
  scale_color_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(
    name = unname(TeX("Change in contributions to overall local sensitivity of $\\,R_0$ \n  from $\\,K_H = 1$ to $\\,K_H = 100$ ")),
    expand = c(0, 0)
  ) +
  facet_rep_grid(
    # rows = vars(sigmaH),
    cols = vars(system_label),
    labeller = labeller(
      system_label = sens_labels,
      # sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
      # KH = as_labeller(appender_KH, default = label_parsed)
    ),
    scales = "free"
  ) +
  guides(linetype = guide_legend(
    title.position = "left",
    title.vjust = 0.5,
    direction = "vertical"
  )) +
  theme_minimal_hgrid(10) +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.position = "bottom",
    legend.justification = 0.5,
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

plot.compzoom_dR0dk
```
# Supplementary Figures

```{r fig-S0_MosquitoDensity, dev = c('pdf','svg', 'png'),  out.width='100%', fig.height=6, fig.width=9, fig.align='center', fig.cap='\\label{fig:MosquitoThermalTraits} Thermal performance curves (TPCs) for the mosquito and parasite traits used in our model. Curves are shown in color for each of the five systems we considered. Temperatures vary from 10\textdegree C to 35\textdegree C to encompass the full thermal niche of all mosquito species considered in this study (defined as the range of temperatures at which all traits for a given species are positive). Each trait is a unimodal function of temperature except for the lifespan of \\textit{Culex quinquefasciatus} (d). Recruitment rate (a) is derived from a sub-model of immature mosquito population dynamics in equations  (2.6) and (2.7. The \\textit{Aedes aegypti} and DENV and \\textit{Ae. aegypti} and ZIKV recruitment rate (a) and maximum biting frequency (b) curves overlap because infection is assumed to not affect these traits (but see Tesla et al. (2018)). All functions and parameters for generating these curves are derived from Mordecai et al., 2013, 2017, 2019; Tesla et al., 2018; Shocket et al., 2020. Shown here are the median values of the mosquito traits with respect to their TPC hyperparameter posterior distributions. A full description of how these curves were obtained is available in Appendix S2: Section S1.'}
## Set up plot dataframe
MosqThermTraits_df <- median.Vec %>% 
  dplyr::select(Temperature, system_ID, `Mosquito population density` = V0)  %>%
  group_by(Temperature, system_ID)

MosqThermTraits_plot <- MosqThermTraits_df %>%
  # Set up plotting variables and theme
  # x = Temperature, y = trait value
  ggplot(mapping = aes(x = Temperature, y = `Mosquito population density`, group = system_ID)) +
  # Plot trait values:
  geom_line(aes(colour = system_ID), size = 1) +
  # x-axis:
  scale_x_continuous(
    name = "Temperature (°C)",
    expand = c(0, 0),
    limits = c(10, 40),
    breaks = seq(10, 40, 2)
  ) +
  # y-axis:
  scale_y_continuous("Equilibrium adult mosquito population density", 
                     expand = c(0.05, 0)) +
  # color:
  scale_color_manual(
    name = "System:",
    values = met.brewer("Egypt", 5, direction = -1),
    labels = function(x) {
      case_when(
        x == "Aedes aegypti / DENV" ~ "*Aedes aegypti* and DENV",
        x == "Aedes aegypti / ZIKV" ~ "*Ae. aegypti* and ZIKV",
        x == "Aedes albopictus / DENV" ~ "*Aedes albopictus* and DENV",
        x == "Anopheles gambiae / Plasmodium falciparum" ~ "*Anopheles gambiae* and *Plasmodium falciparum*",
        x == "Culex quinquefasciatus / WNV" ~ "*Culex quinquefasciatus* and WNV"
      )
    }
  )  +
  # legend:
  guides(color = guide_legend(override.aes = list(size = 4))) +
  # theme options:
  theme_minimal(10) +
  theme(
    legend.margin = margin(),
    legend.text = ggtext::element_markdown(),
    legend.direction = "vertical",
    legend.justification = "center",
    strip.text = element_text(
      face = "bold",
      hjust = 0
    )
  )

MosqThermTraits_plot
```

@@

Topt_estimates_median <- left_join(ToptRM_base_estimates, Topt0_base_estimates) %>%
  select(system_ID, Topt_RM, Topt_0) %>%
  mutate(Topt_diff = Topt_RM - Topt_0) %>%
  mutate(prop_Topt_diff = abs(Topt_diff) / Topt_RM) %>% 
  arrange(system_ID)
```

@@

```{r fig-S8_R0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_unc} The local sensitivity of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$ and $K_H$. Generally, $\\mathcal{R}_0$ is most sensitive to biting frequency, the probability of surviving the extrinsic incubation period, and vector competence. Shown here are the median values of the derivative of $\\mathcal{R}_0$ with respect to each focal mosquito trait across the mosquito trait TPC hyperparameter posterior distributions. Sensitivity values are shown on a logarithmic scale with solid lines indicating positive values and dotted lines indicating negative. Temperatures are restricted to those at which the median of $\\mathcal{R}_0$ is positive for the given system. '}
KH_vals = c(1,100)

@@

dR0dk.df <- data.dR0dT %>% 
  filter(
    KH %in% KH_vals,
    sigmaH %in% unique(data.dR0dT$sigmaH)
  ) %>%
  right_join(select(data.R0, system_ID, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
               filter(KH %in% KH_vals & sigmaH %in% unique(data.dR0dT$sigmaH))) %>%
  # Restrict to relevant temperatures (i.e. where V0 and R0 > 0)
  right_join(temp_lims) %>% 
  group_by(system_ID) %>% 
  filter(Temperature > min_Temp, Temperature < max_Temp) %>% 
  filter(!is.na(median)) %>% 
  ungroup() %>% 
  # Restrict plotted values (so all plots are visible)
  right_join(val_lims) %>% 
  group_by(sigmaH) %>% 
  # filter(median > min_median, median < max_median) %>% 
  ungroup() %>% 
  # filter(median_R0 > 0) %>%
  mutate(abs_median = abs(median)) %>%
  # Normalize values to better tell which is most important
  mutate(sign_median = sign(median)) %>%
  group_by(system_ID, sigmaH, KH) %>%
  mutate(norm_median = ifelse(sign_median>0,
                              abs_median / max(median, na.rm = TRUE),
                              abs_median / min(median, na.rm = TRUE))
         ) %>%
  filter(sign_median != 0, !is.na(sign_median)) %>%
  arrange(sign_median) %>%
  arrange(Temperature)

# NB: in order to produce an R0 TPC, "overall" derivative should go from positive to negative
plot.dR0dk <- dR0dk.df %>%
  # filter(focal_var %in% c("Overall")) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = median, color = focal_var, 
             # linetype = (as.factor(sign_median))
  )) +
  geom_line(lwd = 0.5) +
  geom_hline(yintercept = 0, lwd = 0.25) +
  scale_color_manual(
    name = "Focal trait:",
    values = rev(c(c4a("misc.okabe", 7), "black"))
  ) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(
    name = unname(TeX("Contribution to local temperature sensitivity of $\\,R_0$")),

    expand = c(0, 0)
  ) +
  coord_capped_cart(ylim = c(-1,1)) +
  facet_grid(
    rows = vars(KH, sigmaH),
    cols = vars(system_label),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
      KH = as_labeller(appender_KH, default = label_parsed)
    ),
    scales = "free"
  ) +
  guides(linetype = guide_legend(
    title.position = "left",
    title.vjust = 0.5,
    direction = "vertical"
  )) +
  theme_minimal_hgrid(10) +
  theme(
    panel.spacing = unit(1, "lines"),
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.position = "bottom",
    legend.justification = 0.5,
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@
